---
title: "Basic msaR Usage"
author: "zachcp"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

# Installation

msaR is a an [htmlwidgets](https://github.com/ramnathv/htmlwidgets) wrapper of the [BioJS MSA viewer](https://github.com/wilzbach/msa) javascript library. This package in not on CRAN/Bioconductor and can be installed using [devtools](https://github.com/hadley/devtools):

```{r, eval=FALSE}
devtools::install_github('zachcp/msaR')
```

## Usage

```{r}
library(msaR)

# read some sequences from a Multiple sequence alignment file.
seqfile <- system.file("sequences","AHBA.aln",package="msaR")

# display the MSA.
msaR(seqfile)
```

# Customized MSAs

```{r}
msaR(seqs, menu=F)
```



## Use as a Shiny widget

msaR can be used as a widget with the [Shiny](http://shiny.rstudio.com/) web application framework.

In ui.R
```{r, eval=FALSE}
msaROutput("msa", width="100%")
```

In server.R
```{r, eval=FALSE}
output$msa <- renderMsaR(
  msaR(seqs)
)
```

## Contribute
All contributions are welcome! Please feel free to submit a pull request.

## Support and Suggestions
If you have any problem or suggestion please open an issue [here](https://github.com/zachcp/msaR/issues)

License
-------

This project is licensed under the [Boost Software License 1.0](https://github.com/wilzbach/msa/blob/master/LICENSE).

> Permission is hereby granted, free of charge, to any person or organization
> obtaining a copy of the software and accompanying documentation covered by
> this license (the "Software") to use, reproduce, display, distribute,
> execute, and transmit the Software, and to prepare derivative works of the
> Software, and to permit third-parties to whom the Software is furnished to
> do so, all subject to the following:

If you use the MSAViewer on your website, it solely requires you to link to us
